\documentclass{vldb}

\newcommand{\paperTitle}{Proving Equivalence of SQL Queries Using Satisfiability
Modulo Theories} 
\newcommand{\paperKeywords}{Query Rewriting, Query Optimization, Satisfiability
Modulo Theories}
\newcommand{\paperAuthors}{}

% Define to fix sigplanconf.
% \doi{}

\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}

\usepackage[square,comma,numbers,sort&compress]{natbib}
%\usepackage[hyphens]{url}
\usepackage{hyperref}

% hyperref itself
\hypersetup{
 pdfauthor = {\paperAuthors}, 
 pdftitle = {\paperTitle}, 
 pdfkeywords = {\paperKeywords}, 
 pdfborder={ 0 0 0 }
}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{amsmath,amsopn,amssymb}
\usepackage{subfig}
\usepackage{endnotes,microtype,xspace,graphicx,fancyvrb,multirow}
\usepackage{booktabs}
\usepackage{array,underscore,relsize}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{fancyhdr,lastpage}
\usepackage{enumitem}
% \usepackage[labelfont=bf,font=small,skip=5pt]{caption}

%\usepackage{lmodern}

% aliascnt: counter stuff that works with theorem environments.
\usepackage{aliascnt}

% algorithm2e: algorithms
\usepackage[linesnumbered]{algorithm2e}

% semantic: inference rules
\usepackage{semantic}

% stmaryrd: more math fonts (namely mathbb)
\usepackage{stmaryrd}

% floatrow: putting two figures side by side
\usepackage{floatrow}

\usepackage{mathtools}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{\thepage}

\newcommand{\sys}{\mbox{\textsc{Shara}}\xspace}

% cmds: typesetting commands
\input{cmds}

% std: standard math commands and environments.
\input{std}

% shorthand: paper-specific shorthand commands.
\input{shorthand}
\input{sqlcmd}
% rev: revision information: generated by build system
\input{rev}
\vldbTitle{A Sample Proceedings of the VLDB Endowment Paper in LaTeX Format}
\vldbAuthors{Ben Trovato, G. K. M. Tobin, Lars Th{\sf{\o}}rv{$\ddot{\mbox{a}}$}ld, Lawrence P. Leipuner, Sean Fogarty, Charles Palmer, John Smith, Julius P.~Kumquat, and Ahmet Sacan}
\vldbDOI{https://doi.org/10.14778/xxxxxxx.xxxxxxx}
\vldbVolume{12}
\vldbNumber{xxx}
\vldbYear{2018}

\title{\paperTitle}
\author{\paperAuthors}

\begin{document}

\maketitle

\begin{abstract}

The design of the buffer manager in database management systems (DBMSs)
is influenced by the performance characteristics of volatile
memory (DRAM) and non-volatile storage (e.g., SSD).
The key design assumptions have been that the data must be migrated to DRAM 
for the DBMS to operate on it and that storage is orders of magnitude slower
than DRAM. But the arrival of new non-volatile memory (NVM) technologies that
are nearly as fast as DRAM invalidates these previous assumptions.

This paper presents techniques for managing and designing a multi-tier storage
hierarchy comprising of DRAM, NVM, and SSD.
Our main technical contributions are a multi-tier buffer manager and a storage
system designer that leverage the characteristics of NVM.
We propose a set of optimizations for maximizing the utility of data migration
between different devices in the storage hierarchy. 
We demonstrate that these optimizations have to be tailored based on 
device and workload characteristics. 
Given this, we present a technique for adapting these optimizations to achieve a
near-optimal buffer management policy for an arbitrary workload and storage
hierarchy without requiring any manual tuning.
We finally present a recommendation system for designing a multi-tier storage
hierarchy for a target workload and system cost budget.
Our results show that the NVM-aware buffer manager and storage system designer
improve throughput and reduce system cost across different transaction and
analytical processing workloads.
\end{abstract}

% abstract.tex: DEP, contains abstract
\input{introduction}

\AJ{Need to break down approach into three sections similar to UDP paper. Example:
\begin{enumerate}[noitemsep,nolistsep,label=\protect\BC{\arabic*},leftmargin=7ex]
\setlength{\itemsep}{-0pt}
\item Axiomatic Foundations (?)
\item Aggregates etc.
\item Decision Procedures (?)
\end{enumerate}
}

\input{overview}

\AJ{Problem formalization should come after overview.}
\input{formalize}

% bibliography:
\newcommand{\newblock}{}
\bibliographystyle{abbrv}
\small

\bibliography{p}


\end{document}
